XXX

### 2012-03-24 paper/engNERwiki.tex
DBpedia.

One approach to reduce the manual intervention required in language resource production, and thus ultimately production costs is automatically generating resources. An other approach to achieve this aim is using collaborative annotation and/or collaboratively constructed resources, such as Wikipedia, Wiktionary or Linked Open Data. Researchers apply the Web-as-corpus approach, often dealing with such datasets as Google's Web 1T 5-gram collection or DBPedia.

@@

Despite the aforementioned methods, we applied a new approach to recognize and classify NEs in the corpora generated from Wikipedia. We used the DBpedia ontology classes to map Wikipedia categories to standard NE tags (see more details in section \ref{dbpedia}).

@@

Most authors

The classes in DBpedia are organized into a type hierarchy, available as an OWL (CITE) ontology. The ontology contains the 320 most frequent categories of Wikipedia, arranged into a taxonomy under the base class \texttt{owl:Thing}. Most of the classes belong into the 5 largest sub-hierarchies (here named after their topmost classes XXX): \texttt{Agent} (which is further divided into \texttt{Person} and \texttt{Organisation}), \texttt{Event}, \texttt{Place}, \texttt{Species} and \texttt{Work}. The taxonomy is rather flat: the top level contains 44 classes and there are several nodes with a branching factor of 20.

@@

The full mapping can be found in LINK Appendix A (XXX or not).

@@

>>>>

One approach to reduce the manual intervention required in language resource production, and thus ultimately production costs is automatically generating resources. An other approach to achieve this aim is using collaborative annotation and/or collaboratively constructed resources, such as Wikipedia, Wiktionary or Linked Open Data. Researchers apply the Web-as-corpus approach, often dealing with such datasets as Google's Web 1T 5-gram collection or DBpedia.

@@

In contrast to the aforementioned methods, we applied a new approach to recognize and classify NEs in the corpora generated from Wikipedia. We mapped the DBpedia ontology classes to standard NE tags and assigned them to Wikipedia entities (see more details in section \ref{dbpedia}).

@@

Many authors, such as Kazama and Torisawa \shortcite{Kazama:07} and Nothman et al \shortcite{Nothman:09} used unsupervised methods based on Wikipedia categories and text to classify articles into entity categories. To avoid the inevitable classification errors, we obtain entity type information from the DBpedia knowledge base \cite{Bizer:09}. This enables us to have high precision information about entity types at the expense of recall: out of the 3,903,467 English Wikipedia pages, 1,470,293 are covered by DBpedia.

DBpedia is an open database that presents information about entities in Wikipedia in structured form. Each entity corresponds to a Wikipedia article. DBpedia provides various information about entities including type, properties, home pages, etc. Here we limit our interest to the type system.

The types in DBpedia are organized into a class hierarchy, available as an OWL (CITE) ontology. The ontology contains the 320 most frequent entity categories, arranged into a taxonomy under the base class \texttt{owl:Thing}. Most of the classes belong into the 5 largest sub-hierarchies (here named after their topmost classes XXX): \texttt{Agent} (which is further divided into \texttt{Person} and \texttt{Organisation}), \texttt{Event}, \texttt{Place}, \texttt{Species} and \texttt{Work}. The taxonomy is rather flat: the top level contains 44 classes and there are several nodes with a branching factor of 20.

The type of entities is extracted automatically from Wikipedia categories. However, the mapping between Wikipedia categories and classes in the DBpedia ontology is manually defined. This, together with the fact that the existance of the reference ontology prevents the proliferation of categories observable in Wikipedia \cite{Bizer:09}, ensures that type information in DBpedia can be considered gold quality.

@@

The full mapping can be found in Appendix~\ref{sec:appa}.

@@

\pagebreak
% HEEEEELP!
\appendix
\section{DBpedia to ConLL Mapping}
\label{sec:appa}

\begin{table*}[ht]
\begin{center}
\begin{tabular}{llll}
\hline DBpedia & \bf CoNLL & \bf DBpedia & \bf CoNLL \\ \hline
Person & PER & Library & LOC \\
Place & LOC & MeanOfTransportation & MISC \\
Organization & ORG & PeriodicalLiterature & ORG \\
Organisation & ORG & ProgrammingLanguage & MISC \\
Award & MISC & Project & MISC \\
EthnicGroup & MISC & SportsLeague & MISC \\
Event & MISC & SportsTeamSeason & O \\
Holiday & MISC & Weapon & MISC \\
Ideology & MISC & Work & MISC \\
Language & MISC & & \\
\hline
\end{tabular}
\end{center}
\end{table*}
